```latex
\documentclass{article}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{enumitem}

\begin{document}

\begin{center}
{\Large Rudranil Chowdhury} \\
\href{mailto:rudranilchowdhury83@gmail.com}{rudranilchowdhury83@gmail.com} | +91-8910714765 \\
\href{[GitHub Link]}{GitHub} | \href{ [LinkedIn Link]}{LinkedIn}
\end{center}

\section*{SUMMARY}

Highly motivated B.Tech in Electronics \& Communications Engineering student (Expected Graduation: 2027) with a strong foundation in full-stack web development and a passion for building scalable web applications. Proven ability to design, develop, and deploy complete web solutions, demonstrated through impactful projects using React.js, Node.js, and related technologies. Seeking a Full Stack Development Internship at INLIGHN TECH to contribute to real-world projects and gain hands-on experience.

\section*{EDUCATION}

\textbf{Techno Main Salt Lake, Kolkata} | B.Tech in Electronics \& Communications Engineering | 2023 – 2027 \\
GPA: 8.68/10.0 \\
\textit{Relevant Coursework}: Data Structures and Algorithms, Computer Networks, Object-Oriented Programming, Web Technology

\section*{PROJECTS}

\textbf{AI-Powered SSDLC Automation Platform} | \textit{Next.js, TypeScript, Node.js, Express, Docker, CI/CD} | Apr 2025 – May 2025
\begin{itemize}[leftmargin=*]
    \item Led the development of a modular Work Operating System (Work OS) designed to streamline the Secure Software Development Life Cycle (SSDLC).
    \item Architected the front-end using Next.js and TypeScript and the back-end using Node.js and Express for robust API development, aligning with INLIGHN TECH's focus on these technologies.
    \item Integrated AI models for automated code analysis, vulnerability detection, and documentation generation, resulting in a \textbf{40\% reduction in development time} and a \textbf{60\% improvement in code security assessments} during internal testing.
    \item Implemented CI/CD pipelines with Docker containerization for scalable and reliable deployments, demonstrating proficiency in modern DevOps practices.
\end{itemize}

\textbf{Bail Eligibility Assessment System ("JUDICIO")} | \textit{React, Vite, Node.js, Flask, Docker, YML} | Sep 2024 – Dec 2024
\begin{itemize}[leftmargin=*]
    \item Developed a digital Bail Reckoner System automating bail eligibility assessment for undertrial prisoners.
    \item Engineered a React + Vite front-end and a Node.js + Flask back-end to process \textbf{10,000+ case records}, track imprisonment duration, and evaluate judicial discretion.
    \item Implemented AI-driven decision support, identifying \textbf{85\% of eligible undertrial prisoners}, and integrated i18n for multilingual accessibility across 7+ languages.
    \item Optimized deployment using Docker and YML, achieving a \textbf{40\% reduction in bail processing time} for 200+ legal aid providers and judicial authorities.
\end{itemize}

\textbf{Proctored Women Safety Application ("HERSHIELD")} | \textit{React.js, TailwindCSS, Golang, WebSocket} | Jan 2025 – Mar 2025
\begin{itemize}[leftmargin=*]
    \item Built a full-stack women's safety application with a responsive React.js front-end, achieving \textbf{95+ Lighthouse performance and accessibility scores}.
    \item Developed a WebSocket-based peer-to-peer communication module using a high-performance Golang back-end.
    \item Integrated an NLP-driven speech recognition system to analyze live call/chat transcripts, providing real-time threat ratings with \textbf{87\% accuracy}.
    \item Implemented real-time safe-route navigation using Leaflet.js, aggregating \textbf{500+ crowd-sourced incident data points}.
\end{itemize}

\section*{ACHIEVEMENTS}

\begin{itemize}[leftmargin=*]
    \item \textbf{Grand Finalist, Smart India Hackathon 2024 (Software Edition)}: Selected from over 82,000 participants for innovative solutions, demonstrating problem-solving and rapid prototyping skills.
    \item \textbf{Lead Developer, EDGE 2025 Portfolio Website}: Led a team to build the official website, showcasing leadership, collaboration, and technical excellence under tight deadlines.
\end{itemize}

\section*{SKILLS}

\begin{itemize}[leftmargin=*]
    \item \textbf{Languages}: JavaScript, Python, Java, C++, C, HTML, CSS
    \item \textbf{Frameworks/Libraries}: React.js, Next.js, Node.js, Express, Flask, TailwindCSS
    \item \textbf{Databases}: MongoDB, MySQL, PostgreSQL
    \item \textbf{Tools}: Git, Docker, VS Code, GitHub, CI/CD Pipelines
\end{itemize}

\end{document}
```