```latex
\documentclass{article}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{enumitem}

\begin{document}

\section*{Rudranil Chowdhury}
\href{mailto:rudranilchowdhury83@gmail.com}{rudranilchowdhury83@gmail.com} | +91-8910714765 | \href{https://github.com/}{GitHub} | \href{https://linkedin.com/}{LinkedIn}

\section*{SUMMARY}
Highly motivated B.Tech in Electronics \& Communications Engineering student (Expected Graduation: 2027) with a strong foundation in full-stack web development and a passion for building scalable and innovative solutions. Proven ability to design, develop, and deploy web applications using React, Node.js, and related technologies. Seeking a Full Stack Development Internship at INLIGHN TECH to contribute to real-world projects and further develop my skills.

\section*{EDUCATION}
Techno Main Salt Lake, Kolkata | B.Tech in Electronics \& Communications Engineering | 2023 – 2027 \\
GPA: 8.68/10.0
\begin{itemize}[label=$\bullet$]
    \item Relevant Coursework: Data Structures and Algorithms, Computer Networks, Object-Oriented Programming, Web Technology, Database Management
\end{itemize}

\section*{PROJECTS}
\textbf{AI-Powered SSDLC Automation Platform} | \textit{Next.js, TypeScript, Node.js, Express, Docker, CI/CD} | Apr 2025 – May 2025
\begin{itemize}[label=$\bullet$]
    \item Led the development of a modular Work Operating System (Work OS) to streamline the Secure Software Development Life Cycle (SSDLC), focusing on automation and efficiency.
    \item Architected the front-end using Next.js and TypeScript and the back-end using Node.js and Express, demonstrating full-stack capabilities.
    \item Integrated AI models for automated code analysis and vulnerability detection, resulting in a \textbf{40\% reduction in development time} and a \textbf{60\% improvement in code security assessments} during internal testing.
    \item Implemented CI/CD pipelines with Docker containerization for scalable and reliable deployments, aligning with industry best practices.
\end{itemize}

\textbf{Bail Eligibility Assessment System ("JUDICIO")} | \textit{React, Vite, Node.js, Flask, Docker, MySQL} | Sep 2024 – Dec 2024
\begin{itemize}[label=$\bullet$]
    \item Developed a digital Bail Reckoner System automating bail eligibility assessment, demonstrating proficiency in back-end logic and database management.
    \item Engineered a React + Vite front-end and a Node.js + Flask back-end to process \textbf{10,000+ case records}, track imprisonment duration, and evaluate judicial discretion.
    \item Implemented AI-driven decision support, identifying \textbf{85\% of eligible undertrial prisoners}, and integrated i18n for multilingual accessibility.
    \item Utilized MySQL for database management, showcasing experience with SQL-based systems.
\end{itemize}

\textbf{Proctored Women Safety Application ("HERSHIELD")} | \textit{React.js, TailwindCSS, Golang, Node.js, WebSocket} | Jan 2025 – Mar 2025
\begin{itemize}[label=$\bullet$]
    \item Built a full-stack women's safety application, achieving \textbf{95+ Lighthouse performance and accessibility scores}, demonstrating front-end expertise.
    \item Developed a WebSocket-based peer-to-peer communication module using Golang and Node.js, supporting \textbf{10+ concurrent secure sessions with under 100ms latency}.
    \item Integrated NLP for real-time threat assessment, providing real-time threat ratings with \textbf{87\% accuracy} to recommend safe actions.
\end{itemize}

\section*{ACHIEVEMENTS}
\begin{itemize}[label=$\bullet$]
    \item \textbf{Grand Finalist, Smart India Hackathon 2024 (Software Edition):} Selected from over 82,000 participants for innovative solutions to real-world problems, showcasing problem-solving and teamwork skills.
    \item \textbf{Lead Developer, EDGE 2025 Portfolio Website:} Led a cross-functional team to build the official website, demonstrating leadership, collaboration, and technical excellence under tight deadlines.
\end{itemize}

\section*{SKILLS}
\begin{itemize}[label=$\bullet$]
    \item \textbf{Languages:} JavaScript, Python, Java, HTML, CSS
    \item \textbf{Frameworks/Libraries:} React.js, Node.js, Express, TailwindCSS
    \item \textbf{Databases:} MySQL, MongoDB
    \item \textbf{Tools:} Git, Docker, VS Code, GitHub, REST APIs
\end{itemize}

\end{document}
```