```latex
\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}

\begin{document}

\section*{\LARGE Rudranil Chowdhury}
\href{mailto:rudranilchowdhury83@gmail.com}{rudranilchowdhury83@gmail.com} | +91-8910714765 | \href{https://github.com/[GitHub Link]}{GitHub} | \href{https://linkedin.com/[LinkedIn Link]}{LinkedIn}

\section*{Summary}
Highly motivated B.Tech student with a strong foundation in full-stack web development and a passion for building scalable web applications. Proven ability to design, develop, and deploy complete web solutions using React.js, Node.js, and database technologies. Seeking a Full Stack Development Internship at INLIGHN TECH to gain hands-on experience and contribute to real-world projects.

\section*{Education}
\textbf{Techno Main Salt Lake, Kolkata} | B.Tech, Electronics \& Communications Engineering | 2023 - 2027
\begin{itemize}[leftmargin=*, nosep]
    \item GPA: 8.68/10.0
    \item Relevant Coursework: Data Structures \& Algorithms, Computer Networks, Object-Oriented Programming, Web Technologies, Machine Learning.
\end{itemize}

\section*{Projects}
\textbf{AI-Powered SSDLC Work OS (ZENITH)} | \textit{Next.js, TypeScript, Node.js, Express, MongoDB, Docker} | Apr 2025 - May 2025
\begin{itemize}[leftmargin=*, nosep]
    \item Developed a modular platform to automate and enhance the Secure Software Development Life Cycle (SSDLC).
    \item Architected the frontend with Next.js and the backend with Node.js and Express, integrating MongoDB for data storage.
    \item Integrated AI models for code analysis and vulnerability detection, resulting in a \textbf{40\% reduction} in development time and a \textbf{60\% improvement} in code security assessments during internal testing.
\end{itemize}

\textbf{Bail Reckoner System (JUDICIO)} | \textit{React, Vite, Node.js, Flask, MySQL, Docker} | Sep 2024 - Dec 2024
\begin{itemize}[leftmargin=*, nosep]
    \item Engineered a digital system automating bail eligibility assessment by integrating legal statutes and judicial precedents.
    \item Developed React frontend and Node.js/Flask backend to process \textbf{10,000+} case records, using MySQL for database management.
    \item Flagged \textbf{85\%} of eligible undertrial prisoners using AI-driven decision support, improving efficiency for legal aid providers.
    \item Reduced bail processing time by \textbf{40\%} for \textbf{200+} legal aid providers and judicial authorities.
\end{itemize}

\textbf{Proctored Women Safety App (HERSHIELD)} | \textit{React.js, TailwindCSS, Golang, WebSocket, Leaflet.js} | Jan 2025 - Mar 2025
\begin{itemize}[leftmargin=*, nosep]
    \item Developed a responsive React.js frontend achieving \textbf{95+} Lighthouse performance and accessibility scores.
    \item Implemented a WebSocket-based peer-to-peer communication module with under \textbf{100ms} latency.
    \item Integrated an NLP-driven speech recognition system providing real-time threat ratings with \textbf{87\%} accuracy.
\end{itemize}

\section*{Achievements}
\begin{itemize}[leftmargin=*, nosep]
    \item \textbf{Grand Finalist, Smart India Hackathon 2024 (Software Edition):} Selected from \textbf{82,000+} participants for innovative solutions.
    \item \textbf{Led a team of 4} to build the official portfolio website for EDGE 2025 in 7 days, demonstrating leadership and collaboration.
\end{itemize}

\section*{Skills}
\begin{itemize}[leftmargin=*, nosep]
    \item \textbf{Frontend Development:} React.js, HTML, CSS, JavaScript, TailwindCSS
    \item \textbf{Backend Development:} Node.js, Express, REST APIs
    \item \textbf{Databases:} MongoDB, MySQL
    \item \textbf{Programming Languages:} JavaScript, Python, Java
    \item \textbf{Tools:} Git, Docker, VS Code
\end{itemize}

\end{document}
```